---
title: "Week 4 Data Blitz. Confidence Intervals"
author: "GROUP MEMBER NAMES"
date: "`r format(Sys.Date(), '%B %d, %Y')`"
output:
  html_document:
    toc: true
    toc_float:
      collapsed: false
      smooth_scroll: false
    toc_depth: 2
    theme: cosmo
    highlight: haddock
editor_options:
  chunk_output_type: console
knit: (function(input, ...) rmarkdown::render(input, output_file = xfun::with_ext(basename(input), "html"), output_dir = dirname(input)))
---

```{r include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  message = FALSE,
  warning = FALSE,
  error = TRUE,
  comment = "",
  fig.width = 8,
  fig.height = 5)

options(scipen = 999, width = 80)
```

# 1. Research Question

TYPE YOUR ANSWER HERE

# 2. Packages, Data Import, and Summaries

Your code:

```{r}
# TYPE YOUR CODE HERE
```

# 3. Factor Conversion and Frequency Distribution

Your code:

```{r}
# TYPE YOUR CODE HERE
```

# 4. Full-Sample Confidence Interval

Your code:

```{r}
# TYPE YOUR CODE HERE
```

# 5. Interpretation of the Confidence Limits

TYPE YOUR ANSWER HERE

# 6. Simulation of 100 Sample Means

Your prompt and AI's response:

```
PASTE YOUR PROMPT AND AI'S RESPONSE HERE
```

AI's code:

```{r}
# PASTE AI'S CODE HERE
```

Your inspection of AI's comments:

TYPE YOUR ANSWER HERE

# 7. Explanation of the Standard Error

TYPE YOUR ANSWER HERE

# 8. Simulation With 95% Confidence Intervals

Your prompt and AI's response:

```
PASTE YOUR PROMPT AND AI'S RESPONSE HERE
```

AI's code:

```{r}
# PASTE AI'S CODE HERE
```

# 9. Explanation of 95% Confidence

TYPE YOUR ANSWER HERE

# 10. Descriptives and Confidence Intervals by Group

Your code:

```{r}
# TYPE YOUR CODE HERE
```

# 11. Differences in Confidence Interval Width

Your prompt and AI's response:

```
PASTE YOUR PROMPT AND AI'S RESPONSE HERE
```

The width of each group's interval and why the widths are similar or different:

TYPE YOUR ANSWER HERE

# 12. Comparison of the Groups

TYPE YOUR ANSWER HERE

# 13. Reflection on AI

TYPE YOUR ANSWER HERE
