---
title: "Week 3 Data Blitz: Sampling Error"
author: "GROUP MEMBER NAMES"
date: "`r format(Sys.Date(), '%B %d, %Y')`"
output:
  html_document:
    toc: true
    toc_float:
      collapsed: false
      smooth_scroll: false
    toc_depth: 2
    theme: cosmo
    highlight: haddock
editor_options:
  chunk_output_type: console
knit: (function(input, ...) rmarkdown::render(input, output_file = xfun::with_ext(basename(input), "html"), output_dir = dirname(input)))
---

```{r include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  message = FALSE,
  warning = FALSE,
  error = TRUE,
  comment = "",
  fig.width = 8,
  fig.height = 5)

options(scipen = 999, width = 80)
```

# Loading Packages

```{r}
library(psych)
```

# Reading the Data

```{r}
filepath <- "https://raw.githubusercontent.com/craigenders/psych250a/main/data/Cancer.csv"
blitz <- read.csv(filepath, stringsAsFactors = TRUE)
```

# 1. Standard Error of the Depression Mean

Your code:

```{r}
# TYPE YOUR CODE HERE
```

Whether your calculation agrees with the descriptive statistics output, what the standard error quantifies, what a sampling distribution is, and how the standard error relates to that distribution:

TYPE YOUR ANSWER HERE

# 2. Central Limit Theorem Predictions

What the central limit theorem predicts about the shape, center, and spread of the sampling distribution, and what you predict you will observe:

TYPE YOUR ANSWER HERE

# 3. Audit of the Simulation Code

AI's response:

```
PASTE AI'S RESPONSE HERE
```

Your explanation of the simulation's goal and major steps:

TYPE YOUR ANSWER HERE

# 4. Running the Simulation

The simulation code is below. Run the chunk as it is written.

```{r}
# ---------------------------------------------------------------------
# SAMPLING ERROR SIMULATION
# ---------------------------------------------------------------------

# SIMULATION INPUTS ----

pop_mean <- 16        # population mean
pop_sd <- 11.44       # population standard deviation
sample_N <- 299       # sample size

# ---------------------------------------------------------------------
# SIMULATION CODE
# ---------------------------------------------------------------------

# VERIFICATION AUDIT ----

# makes the results identical every time the script is run
set.seed(250)

# draw a single sample of scores from the population
mysample <- rnorm(n = sample_N, mean = pop_mean, sd = pop_sd)

# mean, standard deviation, skewness, and excess kurtosis of the sample
audit_mean <- mean(mysample)
audit_sd <- sd(mysample)
audit_skew <- mean((mysample - audit_mean)^3) / audit_sd^3
audit_kurt <- mean((mysample - audit_mean)^4) / audit_sd^4 - 3

# tallest bar in the audit histogram, used to leave room for the legend
audit_barheight <- max(hist(mysample, breaks = 25, plot = FALSE)$counts)

# graph the sample
hist(mysample, breaks = 25,
     ylim = c(0, audit_barheight * 1.35),
     main = paste('Verification Audit: One Sample of Size =', sample_N),
     xlab = 'Scores')

legend('topright', bty = 'n',
       legend = c(paste('Mean =', round(audit_mean, 3)),
                  paste('SD =', round(audit_sd, 3)),
                  paste('Skewness =', round(audit_skew, 3)),
                  paste('Excess kurtosis =', round(audit_kurt, 3))))

# DRAW 100,000 RANDOM SAMPLES ----

# create an empty vector to hold the 100,000 sample means
samplemeans <- rep(0, 100000)

# draw a sample, compute its mean, and store the mean; repeat 100,000 times
for(s in 1:100000){
  sampledata <- rnorm(n = sample_N, mean = pop_mean, sd = pop_sd)
  samplemeans[s] <- mean(sampledata)
}

# EXAMINE THE SAMPLING DISTRIBUTION ----

# horizontal axis half-width
plot_halfwidth <- 4

# histogram bin width, also held constant so the bars are comparable
bin_width <- 0.05

# vertical axis maximum, held constant so bar heights are comparable
plot_maxcount <- 6000

# graph the 100,000 sample means with fixed bin width and axis ranges so graphs are comparable
hist(samplemeans,
     breaks = seq(pop_mean - 50, pop_mean + 50, by = bin_width),
     xlim = c(pop_mean - plot_halfwidth, pop_mean + plot_halfwidth),
     ylim = c(0, plot_maxcount),
     main = 'Distribution of 100,000 Sample Means',
     xlab = 'Sample Means')

legend(x = pop_mean + plot_halfwidth, y = plot_maxcount, xjust = 1, yjust = 1, bty = 'n',
       legend = c(paste('N =', sample_N),
                  paste('Mean of the sample means =', round(mean(samplemeans), 3)),
                  paste('SD of the sample means =', round(sd(samplemeans), 3)),
                  paste('Standard error formula =', round(pop_sd / sqrt(sample_N), 3))))
```

Whether the sampling distribution is consistent with your predictions from Question 2, and how the standard deviation of the 100,000 sample means compares with the standard error from Question 1:

TYPE YOUR ANSWER HERE

# 5. How Unusual Is a Sample Mean of 14.85?

TYPE YOUR ANSWER HERE

# 6. Prediction for a Less Variable Population

What should happen to the shape, center, and spread of the sampling distribution when the population standard deviation is reduced from 11.44 to 6:

TYPE YOUR ANSWER HERE

# 7. AI on Variability and Sampling Error

Your prompt:

PASTE YOUR PROMPT HERE

AI's response:

```
PASTE AI'S RESPONSE HERE
```

Whether AI's response supports or contradicts your prediction from Question 6:

TYPE YOUR ANSWER HERE

# 8. Simulation With a Smaller Population Standard Deviation

The simulation code is below. The only change is the population standard deviation.

```{r}
# ---------------------------------------------------------------------
# SAMPLING ERROR SIMULATION
# ---------------------------------------------------------------------

# SIMULATION INPUTS ----

pop_mean <- 16        # population mean
pop_sd <- 6           # population standard deviation
sample_N <- 299       # sample size

# ---------------------------------------------------------------------
# SIMULATION CODE
# ---------------------------------------------------------------------

# VERIFICATION AUDIT ----

# makes the results identical every time the script is run
set.seed(250)

# draw a single sample of scores from the population
mysample <- rnorm(n = sample_N, mean = pop_mean, sd = pop_sd)

# mean, standard deviation, skewness, and excess kurtosis of the sample
audit_mean <- mean(mysample)
audit_sd <- sd(mysample)
audit_skew <- mean((mysample - audit_mean)^3) / audit_sd^3
audit_kurt <- mean((mysample - audit_mean)^4) / audit_sd^4 - 3

# tallest bar in the audit histogram, used to leave room for the legend
audit_barheight <- max(hist(mysample, breaks = 25, plot = FALSE)$counts)

# graph the sample
hist(mysample, breaks = 25,
     ylim = c(0, audit_barheight * 1.35),
     main = paste('Verification Audit: One Sample of Size =', sample_N),
     xlab = 'Scores')

legend('topright', bty = 'n',
       legend = c(paste('Mean =', round(audit_mean, 3)),
                  paste('SD =', round(audit_sd, 3)),
                  paste('Skewness =', round(audit_skew, 3)),
                  paste('Excess kurtosis =', round(audit_kurt, 3))))

# DRAW 100,000 RANDOM SAMPLES ----

# create an empty vector to hold the 100,000 sample means
samplemeans <- rep(0, 100000)

# draw a sample, compute its mean, and store the mean; repeat 100,000 times
for(s in 1:100000){
  sampledata <- rnorm(n = sample_N, mean = pop_mean, sd = pop_sd)
  samplemeans[s] <- mean(sampledata)
}

# EXAMINE THE SAMPLING DISTRIBUTION ----

# horizontal axis half-width
plot_halfwidth <- 4

# histogram bin width, also held constant so the bars are comparable
bin_width <- 0.05

# vertical axis maximum, held constant so bar heights are comparable
plot_maxcount <- 6000

# graph the 100,000 sample means with fixed bin width and axis ranges so graphs are comparable
hist(samplemeans,
     breaks = seq(pop_mean - 50, pop_mean + 50, by = bin_width),
     xlim = c(pop_mean - plot_halfwidth, pop_mean + plot_halfwidth),
     ylim = c(0, plot_maxcount),
     main = 'Distribution of 100,000 Sample Means',
     xlab = 'Sample Means')

legend(x = pop_mean + plot_halfwidth, y = plot_maxcount, xjust = 1, yjust = 1, bty = 'n',
       legend = c(paste('N =', sample_N),
                  paste('Mean of the sample means =', round(mean(samplemeans), 3)),
                  paste('SD of the sample means =', round(sd(samplemeans), 3)),
                  paste('Standard error formula =', round(pop_sd / sqrt(sample_N), 3))))
```

Your comparison with the distribution from Question 4, whether your predictions were correct, and whether the standard error formula agrees with the standard deviation of the 100,000 sample means:

TYPE YOUR ANSWER HERE
