---
title: "Week 7 Data Blitz. Independent-Samples t-Test"
author: "GROUP MEMBER NAMES"
date: "`r format(Sys.Date(), '%B %d, %Y')`"
output:
  html_document:
    toc: true
    toc_float:
      collapsed: false
      smooth_scroll: false
    toc_depth: 2
    theme: cosmo
    highlight: haddock
editor_options:
  chunk_output_type: console
knit: (function(input, ...) rmarkdown::render(input, output_file = xfun::with_ext(basename(input), "html"), output_dir = dirname(input)))
---

```{r include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  message = FALSE,
  warning = FALSE,
  error = TRUE,
  comment = "",
  fig.width = 8,
  fig.height = 5)

options(scipen = 999, width = 80)
```

# 1. Research Question

TYPE YOUR ANSWER HERE

# 2. Packages, Data Import, and Factor Conversion

Your code:

```{r}
# TYPE YOUR CODE HERE
```

# 3. Descriptive Statistics by Group

Your code:

```{r}
# TYPE YOUR CODE HERE
```

# 4. Evaluation of the Mean Difference

TYPE YOUR ANSWER HERE

# 5. Standard Error

Your code:

```{r}
# TYPE YOUR CODE HERE
```

Your explanation of the standard error and how it refines your conclusion from Task 4:

TYPE YOUR ANSWER HERE

# 6. Independent-Samples *t*-Test and Effect Size

Your code:

```{r}
# TYPE YOUR CODE HERE
```

# 7. Interpretation of the *p*-Value

TYPE YOUR ANSWER HERE

# 8. Interpretation of the Confidence Interval

TYPE YOUR ANSWER HERE

# 9. Welch’s and Student’s *t*-Tests

Your prompt and AI's response:

```
PASTE YOUR PROMPT AND AI'S RESPONSE HERE
```

Your one-paragraph summary:

TYPE YOUR ANSWER HERE

# 10. Within-Group Normality

Your code:

```{r}
# TYPE YOUR CODE HERE
```

Your evaluation of within-group normality:

TYPE YOUR ANSWER HERE

# 11. Answer to the Research Question

TYPE YOUR ANSWER HERE

# 12. Reflection on AI

TYPE YOUR ANSWER HERE
