---
title: "Week 6 Data Blitz. Paired-Samples t-Test"
author: "GROUP MEMBER NAMES"
date: "`r format(Sys.Date(), '%B %d, %Y')`"
output:
  html_document:
    toc: true
    toc_float:
      collapsed: false
      smooth_scroll: false
    toc_depth: 2
    theme: cosmo
    highlight: haddock
editor_options:
  chunk_output_type: console
knit: (function(input, ...) rmarkdown::render(input, output_file = xfun::with_ext(basename(input), "html"), output_dir = dirname(input)))
---

```{r include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  message = FALSE,
  warning = FALSE,
  error = TRUE,
  comment = "",
  fig.width = 8,
  fig.height = 5)

options(scipen = 999, width = 80)
```

# 1. Research Question

TYPE YOUR ANSWER HERE

# 2. Packages, Data Import, and Summaries

Your code:

```{r}
# TYPE YOUR CODE HERE
```

# 3. Descriptive Statistics

TYPE YOUR ANSWER HERE

# 4. Paired-Samples *t*-Test

Your code:

```{r}
# TYPE YOUR CODE HERE
```

# 5. Assumptions of the Paired-Samples *t*-Test

AI's response:

```
PASTE AI'S RESPONSE HERE
```

AI's code:

```{r}
# PASTE AI'S CODE HERE
```

Discrepancies between AI's code comments and its explanation of the assumptions:

TYPE YOUR ANSWER HERE

Your judgment about each assumption and whether any violations threaten the validity of your results:

TYPE YOUR ANSWER HERE

# 6. Standard Error

Your code:

```{r}
# TYPE YOUR CODE HERE
```

Your explanation of the standard error:

TYPE YOUR ANSWER HERE

# 7. Interpretation of the Confidence Interval

TYPE YOUR ANSWER HERE

# 8. Evaluation of the Null Hypothesis

TYPE YOUR ANSWER HERE

# 9. The *p*-Value as a Conditional Probability

AI's response:

```
PASTE AI'S RESPONSE HERE
```

Your interpretation of the *p*-value:

TYPE YOUR ANSWER HERE

# 10. Explanation of the *t* Statistic

TYPE YOUR ANSWER HERE

# 11. Effect Size

Your code:

```{r}
# TYPE YOUR CODE HERE
```

# 12. Interpretation of the Effect Size

TYPE YOUR ANSWER HERE

# 13. Comparison of the *p*-Value and the Effect Size

TYPE YOUR ANSWER HERE

# 14. Reflection on AI

TYPE YOUR ANSWER HERE
