---
title: "Psych 250a — Week 2 Assignment. Descriptive Statistics"
author: "YOUR NAME HERE"
date: "`r format(Sys.Date(), '%B %d, %Y')`"
output:
  pdf_document:
    toc: true
    toc_depth: 3
    latex_engine: xelatex
  html_document:
    toc: true
    toc_float:
      collapsed: false
      smooth_scroll: false
    toc_depth: 3
    theme: cosmo
    highlight: haddock
header-includes:
  - \usepackage{fvextra}
  - \DefineVerbatimEnvironment{Highlighting}{Verbatim}{breaklines,breakanywhere,commandchars=\\\{\}}
  - \fvset{breaklines=true, breakanywhere=true}
  - \RecustomVerbatimEnvironment{verbatim}{Verbatim}{breaklines,breakanywhere}
editor_options:
  chunk_output_type: console
---

```{r include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  message = FALSE,
  warning = FALSE,
  error = TRUE,
  comment = "",
  fig.width = 8,
  fig.height = 5)

options(scipen = 999, width = 80)
```

# Question 1: Import and Summarize the Data

```{r}
# TYPE YOUR CODE HERE
```

# Question 2: Convert ADHD and Male to Factors

Your code:

```{r}
# TYPE YOUR CODE HERE
```

# Question 3: Group Comparison Graphs and Descriptive Statistics

Your code:

```{r}
# TYPE YOUR CODE HERE
```

# Question 4: AlphaEEG Mean Versus Median

TYPE YOUR ANSWER HERE

# Question 5: Attention Group Means and Standard Deviations

TYPE YOUR ANSWER HERE

# Question 6: AI on t-Test Conditions

Your evaluation of which outcome more closely satisfies the conditions, and why:

TYPE YOUR ANSWER HERE

# Question 7: Explain the Standard Deviation

Your original passage:

TYPE YOUR ANSWER HERE

Whether you accepted or rejected AI's evaluation of each requirement, and why:

TYPE YOUR ANSWER HERE

Your revised passage:

TYPE YOUR ANSWER HERE

# Question 8: z-Scores

Your code:

```{r}
# TYPE YOUR CODE HERE
```

Whether and how your results align with AI's predictions:

TYPE YOUR ANSWER HERE

# Question 9: Comparing Standardized Group Differences

Your code:

```{r}
# TYPE YOUR CODE HERE
```

Your conclusion about which measure shows more pronounced ADHD-related differences:

TYPE YOUR ANSWER HERE

# Question 10: Chat Log

`````
PASTE YOUR CHAT LOG HERE
`````
