---
title: "Psych 250a — Week 0 Assignment: Intro to R"
author: "YOUR NAME HERE"
date: "`r format(Sys.Date(), '%B %d, %Y')`"
output:
  pdf_document:
    toc: true
    toc_depth: 3
    latex_engine: xelatex
  html_document:
    toc: true
    toc_float:
      collapsed: false
      smooth_scroll: false
    toc_depth: 3
    theme: cosmo
    highlight: haddock
header-includes:
  - \usepackage{fvextra}
  - \DefineVerbatimEnvironment{Highlighting}{Verbatim}{breaklines,breakanywhere,commandchars=\\\{\}}
  - \fvset{breaklines=true, breakanywhere=true}
  - \RecustomVerbatimEnvironment{verbatim}{Verbatim}{breaklines,breakanywhere}
editor_options:
  chunk_output_type: console
---

```{r include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  message = FALSE,
  warning = FALSE,
  error = TRUE,
  comment = "",
  fig.width = 8,
  fig.height = 5)

options(scipen = 999, width = 80)
```

```{r}
library(psych)
library(summarytools)
```

```{r}
# Reads the data from the course repository. Requires an internet connection.
file_url <- "https://raw.githubusercontent.com/craigenders/psych250a/main/data/assignment0.csv"
assign0 <- read.csv(file_url, stringsAsFactors = TRUE)

# To work offline instead, save assignment0.csv to the same folder as this script
# Comment out the lines that read the data from online repository
# Remove the hashtag from the three lines below
# library(rstudioapi)
# setwd(dirname(getActiveDocumentContext()$path))
# assign0 <- read.csv("assignment0.csv", stringsAsFactors = TRUE)
```

# Question 1: Sum-score prompt

AI's response:

```
PASTE AI'S RESPONSE HERE
```

Your prompt:

PASTE YOUR PROMPT HERE

AI's code:

```{r}
# PASTE AI'S CODE HERE
```

# Question 2: Audit of sum-score code

a. Which part of the code selects depress1 to depress7?

TYPE YOUR ANSWER HERE

b. Which part sums the seven variables separately for each participant?

TYPE YOUR ANSWER HERE

c. Which part produces a missing sum score (NA) if any of the seven items
is missing?

TYPE YOUR ANSWER HERE

d. Which part adds the sum score named depression to the data frame?

TYPE YOUR ANSWER HERE

# Question 3: Verification prompt

AI's response:

```
PASTE AI'S RESPONSE HERE
```

Your prompt:

PASTE YOUR PROMPT HERE

AI's code:

```{r}
# PASTE AI'S CODE HERE
```

# Question 4: Explanation of verification code

What does the code for Check 1 do?

TYPE YOUR ANSWER HERE

What does the code for Check 2 do?

TYPE YOUR ANSWER HERE

# Question 5: Clinical-depression recode prompt

Your prompt:

PASTE YOUR PROMPT HERE

AI's code:

```{r}
# PASTE AI'S CODE HERE
```

# Question 6: Factor-conversion code

Your code:

```{r}
# TYPE YOUR CODE HERE
```

# Question 7: AI audit and verification of factor code

Your prompt:

PASTE YOUR PROMPT HERE

AI's response:

```
PASTE AI'S RESPONSE HERE
```

AI's code:

```{r}
# PASTE AI'S CODE HERE
```
