---
title: "Psych 250a — Week 3 Assignment: Sampling Error"
author: "YOUR NAME HERE"
date: "`r format(Sys.Date(), '%B %d, %Y')`"
output:
  pdf_document:
    toc: true
    toc_depth: 3
    latex_engine: xelatex
  html_document:
    toc: true
    toc_float:
      collapsed: false
      smooth_scroll: false
    toc_depth: 3
    theme: cosmo
    highlight: haddock
header-includes:
  - \usepackage{fvextra}
  - \DefineVerbatimEnvironment{Highlighting}{Verbatim}{breaklines,breakanywhere,commandchars=\\\{\}}
  - \fvset{breaklines=true, breakanywhere=true}
  - \RecustomVerbatimEnvironment{verbatim}{Verbatim}{breaklines,breakanywhere}
editor_options:
  chunk_output_type: console
---

```{r include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  message = FALSE,
  warning = FALSE,
  error = TRUE,
  comment = "",
  fig.width = 8,
  fig.height = 5)

options(scipen = 999, width = 80)
```

```{r}
library(ggplot2)
library(psych)
library(summarytools)
```

```{r}
# Reads the data from the course repository. Requires an internet connection.
file_url <- "https://raw.githubusercontent.com/craigenders/psych250a/main/data/assignment2.csv"
assign2 <- read.csv(file_url, stringsAsFactors = TRUE)

# To work offline instead, save assignment2.csv to the same folder as this script
# Comment out the lines that read the data from online repository
# Remove the hashtag from the three lines below
# library(rstudioapi)
# setwd(dirname(getActiveDocumentContext()$path))
# assign2 <- read.csv("assignment2.csv", stringsAsFactors = TRUE)
```

# Question 1: Standard Error of the Attention Mean

Your code:

```{r}
# TYPE YOUR CODE HERE
```

Whether your calculation agrees with the descriptive statistics output:

TYPE YOUR ANSWER HERE

# Question 2: Explain the Standard Error

Your original passage:

TYPE YOUR ANSWER HERE

AI's response:

```
PASTE AI'S RESPONSE HERE
```

Whether you accepted or rejected AI's evaluation of each requirement, and why:

TYPE YOUR ANSWER HERE

Your revised passage:

TYPE YOUR ANSWER HERE

# Question 3: Standard Deviation Versus Standard Error

TYPE YOUR ANSWER HERE

# Question 4: AI on the Central Limit Theorem

AI's response:

```
PASTE AI'S RESPONSE HERE
```

# Question 5: Audit the Simulation Code

AI's response:

```
PASTE AI'S RESPONSE HERE
```

# Question 6: Run the Simulation

The simulation code is below. Run the chunk as it is written.

```{r}
# ---------------------------------------------------------------------
# SAMPLING ERROR SIMULATION
# ---------------------------------------------------------------------

# SIMULATION INPUTS ----

pop_mean <- 27        # population mean
pop_sd <- 10.10       # population standard deviation
sample_N <- 939       # sample size

# ---------------------------------------------------------------------
# SIMULATION CODE
# ---------------------------------------------------------------------

# VERIFICATION AUDIT ----

# makes the results identical every time the script is run
set.seed(250)

# draw a single sample of scores from the population
mysample <- rnorm(n = sample_N, mean = pop_mean, sd = pop_sd)

# mean, standard deviation, skewness, and excess kurtosis of the sample
audit_mean <- mean(mysample)
audit_sd <- sd(mysample)
audit_skew <- mean((mysample - audit_mean)^3) / audit_sd^3
audit_kurt <- mean((mysample - audit_mean)^4) / audit_sd^4 - 3

# tallest bar in the audit histogram, used to leave room for the legend
audit_barheight <- max(hist(mysample, breaks = 25, plot = FALSE)$counts)

# graph the sample
hist(mysample, breaks = 25,
     ylim = c(0, audit_barheight * 1.35),
     main = paste('Verification Audit: One Sample of Size =', sample_N),
     xlab = 'Scores')

legend('topright', bty = 'n',
       legend = c(paste('Mean =', round(audit_mean, 3)),
                  paste('SD =', round(audit_sd, 3)),
                  paste('Skewness =', round(audit_skew, 3)),
                  paste('Excess kurtosis =', round(audit_kurt, 3))))

# DRAW 100,000 RANDOM SAMPLES ----

# create an empty vector to hold the 100,000 sample means
samplemeans <- rep(0, 100000)

# draw a sample, compute its mean, and store the mean; repeat 100,000 times
for(s in 1:100000){
  sampledata <- rnorm(n = sample_N, mean = pop_mean, sd = pop_sd)
  samplemeans[s] <- mean(sampledata)
}

# EXAMINE THE SAMPLING DISTRIBUTION ----

# horizontal axis half-width
plot_halfwidth <- 5

# histogram bin width, also held constant so the bars are comparable
bin_width <- 0.05

# vertical axis maximum, held constant so bar heights are comparable
plot_maxcount <- 8000

# graph the 100,000 sample means with fixed bin width and axis ranges so graphs are comparable
hist(samplemeans,
     breaks = seq(pop_mean - 50, pop_mean + 50, by = bin_width),
     xlim = c(pop_mean - plot_halfwidth, pop_mean + plot_halfwidth),
     ylim = c(0, plot_maxcount),
     main = 'Distribution of 100,000 Sample Means',
     xlab = 'Sample Means')

legend('topright', bty = 'n',
       legend = c(paste('N =', sample_N),
                  paste('Mean of the sample means =', round(mean(samplemeans), 3)),
                  paste('SD of the sample means =', round(sd(samplemeans), 3)),
                  paste('Standard error formula =', round(pop_sd / sqrt(sample_N), 3))))
```

Whether the sampling distribution is consistent with the central limit theorem predictions from Question 4:

TYPE YOUR ANSWER HERE

# Question 7: Reduce the Sample Size

Your prediction about the center, shape, and spread at a sample size of 100:

TYPE YOUR ANSWER HERE

The simulation code is below. The only change is the sample size.

```{r}
# ---------------------------------------------------------------------
# SAMPLING ERROR SIMULATION
# ---------------------------------------------------------------------

# SIMULATION INPUTS ----

pop_mean <- 27        # population mean
pop_sd <- 10.10       # population standard deviation
sample_N <- 100       # sample size

# ---------------------------------------------------------------------
# SIMULATION CODE
# ---------------------------------------------------------------------

# VERIFICATION AUDIT ----

# makes the results identical every time the script is run
set.seed(250)

# draw a single sample of scores from the population
mysample <- rnorm(n = sample_N, mean = pop_mean, sd = pop_sd)

# mean, standard deviation, skewness, and excess kurtosis of the sample
audit_mean <- mean(mysample)
audit_sd <- sd(mysample)
audit_skew <- mean((mysample - audit_mean)^3) / audit_sd^3
audit_kurt <- mean((mysample - audit_mean)^4) / audit_sd^4 - 3

# tallest bar in the audit histogram, used to leave room for the legend
audit_barheight <- max(hist(mysample, breaks = 25, plot = FALSE)$counts)

# graph the sample
hist(mysample, breaks = 25,
     ylim = c(0, audit_barheight * 1.35),
     main = paste('Verification Audit: One Sample of Size =', sample_N),
     xlab = 'Scores')

legend('topright', bty = 'n',
       legend = c(paste('Mean =', round(audit_mean, 3)),
                  paste('SD =', round(audit_sd, 3)),
                  paste('Skewness =', round(audit_skew, 3)),
                  paste('Excess kurtosis =', round(audit_kurt, 3))))

# DRAW 100,000 RANDOM SAMPLES ----

# create an empty vector to hold the 100,000 sample means
samplemeans <- rep(0, 100000)

# draw a sample, compute its mean, and store the mean; repeat 100,000 times
for(s in 1:100000){
  sampledata <- rnorm(n = sample_N, mean = pop_mean, sd = pop_sd)
  samplemeans[s] <- mean(sampledata)
}

# EXAMINE THE SAMPLING DISTRIBUTION ----

# horizontal axis half-width
plot_halfwidth <- 5

# histogram bin width, also held constant so the bars are comparable
bin_width <- 0.05

# vertical axis maximum, held constant so bar heights are comparable
plot_maxcount <- 8000

# graph the 100,000 sample means with fixed bin width and axis ranges so graphs are comparable
hist(samplemeans,
     breaks = seq(pop_mean - 50, pop_mean + 50, by = bin_width),
     xlim = c(pop_mean - plot_halfwidth, pop_mean + plot_halfwidth),
     ylim = c(0, plot_maxcount),
     main = 'Distribution of 100,000 Sample Means',
     xlab = 'Sample Means')

legend('topright', bty = 'n',
       legend = c(paste('N =', sample_N),
                  paste('Mean of the sample means =', round(mean(samplemeans), 3)),
                  paste('SD of the sample means =', round(sd(samplemeans), 3)),
                  paste('Standard error formula =', round(pop_sd / sqrt(sample_N), 3))))
```

Your evaluation of the predictions, including whether the standard deviation of the 100,000 sample means is consistent with the standard error formula:

TYPE YOUR ANSWER HERE

# Question 8: AI on Skewed Populations

AI's response:

```
PASTE AI'S RESPONSE HERE
```

# Question 9: Modify the Simulation for a Skewed Population

AI's code:

```{r}
# PASTE AI'S CODE HERE
```

# Question 10: Audit the AI-Generated Code

TYPE YOUR ANSWER HERE

# Question 11: Compare the Two Sampling Distributions

TYPE YOUR ANSWER HERE
