---
title: "Psych 250a — Week 0 Assignment. Introduction to R"
author: "YOUR NAME HERE"
date: "`r format(Sys.Date(), '%B %d, %Y')`"
output:
  pdf_document:
    toc: true
    toc_depth: 3
    latex_engine: xelatex
  html_document:
    toc: true
    toc_float:
      collapsed: false
      smooth_scroll: false
    toc_depth: 3
    theme: cosmo
    highlight: haddock
header-includes:
  - \usepackage{fvextra}
  - \DefineVerbatimEnvironment{Highlighting}{Verbatim}{breaklines,breakanywhere,commandchars=\\\{\}}
  - \fvset{breaklines=true, breakanywhere=true}
  - \RecustomVerbatimEnvironment{verbatim}{Verbatim}{breaklines,breakanywhere}
editor_options:
  chunk_output_type: console
---

```{r include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  message = FALSE,
  warning = FALSE,
  error = TRUE,
  comment = "",
  fig.width = 8,
  fig.height = 5)

options(scipen = 999, width = 80)
```

# Question 1: Import and Summarize the Data

```{r}
# TYPE YOUR CODE HERE
```

# Question 2: Decisions About the Depression Sum Score

Your explanation of which recommendations dictate how the sum score is computed, and why:

TYPE YOUR ANSWER HERE

# Question 3: AI Prompt for Sum Score


AI's code:

```{r}
# PASTE AI'S CODE HERE
```

# Question 4: Audit the Sum Score Code


a. Which part of the code selects `Depress1` to `Depress7`?

TYPE YOUR ANSWER HERE

b. Which part sums the seven variables separately for each participant?

TYPE YOUR ANSWER HERE

c. Which part produces a missing sum score (`NA`) if any of the seven items
is missing?

TYPE YOUR ANSWER HERE

d. Which part adds the sum score named `Depression` to the data frame?

TYPE YOUR ANSWER HERE

# Question 5: AI Prompt for Verification Checks


AI's code:

```{r}
# PASTE AI'S CODE HERE
```

# Question 6: Explain the Verification Code


Codebook paragraph for Check 1:

TYPE YOUR ANSWER HERE

Codebook paragraph for Check 2:

TYPE YOUR ANSWER HERE

# Question 7: Recode Depression into a Binary Variable


Your code:

```{r}
# TYPE YOUR CODE HERE
```

# Question 8: Convert Binary Variables to Factors


Your code:

```{r}
# TYPE YOUR CODE HERE
```

# Question 9: AI Review of Recoding and Factor Code


AI's verification code:

```{r}
# PASTE AI'S CODE HERE
```

Your statement about what the verification shows:

TYPE YOUR ANSWER HERE

# Question 10: Chat Log

`````
PASTE YOUR CHAT LOG HERE
`````
