---
title: "Psych 250a — Week 6 Assignment. Paired-Samples t-Test"
author: "YOUR NAME HERE"
date: "`r format(Sys.Date(), '%B %d, %Y')`"
output:
  pdf_document:
    toc: true
    toc_depth: 3
    latex_engine: xelatex
  html_document:
    toc: true
    toc_float:
      collapsed: false
      smooth_scroll: false
    toc_depth: 3
    theme: cosmo
    highlight: haddock
header-includes:
  - \usepackage{fvextra}
  - \DefineVerbatimEnvironment{Highlighting}{Verbatim}{breaklines,breakanywhere,commandchars=\\\{\}}
  - \fvset{breaklines=true, breakanywhere=true}
  - \RecustomVerbatimEnvironment{verbatim}{Verbatim}{breaklines,breakanywhere}
editor_options:
  chunk_output_type: console
---

```{r include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  message = FALSE,
  warning = FALSE,
  error = TRUE,
  comment = "",
  fig.width = 8,
  fig.height = 5)

options(scipen = 999, width = 80)
```

# Question 1: Import and Summarize the Data

Your code:

```{r}
# TYPE YOUR CODE HERE
```

# Question 2: Convert Male and Drug to Factors

Your code:

```{r}
# TYPE YOUR CODE HERE
```

# Question 3: Group-by-Time Interaction

The pattern of means you would expect with and without a group-by-time interaction:

TYPE YOUR ANSWER HERE

# Question 4: AI Prompt for the Line Graph

AI's code:

```{r}
# PASTE AI'S CODE HERE
```

# Question 5: Explain the Graph Code

Your explanation of how the code works and what you learned:

TYPE YOUR ANSWER HERE

# Question 6: Evaluate the Interaction in the Graph

Your evaluation of whether the graph suggests a group-by-time interaction:

TYPE YOUR ANSWER HERE

# Question 7: Subset the Data by Medication Group

Your code:

```{r}
# TYPE YOUR CODE HERE
```

Your explanation of how the outputs confirm (or fail to confirm) the subsets:

TYPE YOUR ANSWER HERE

# Question 8: Paired-Samples *t*-Tests

Your code:

```{r}
# TYPE YOUR CODE HERE
```

# Question 9: Report the Results in APA Format

Your APA-style passage:

TYPE YOUR ANSWER HERE

# Question 10: Comparing Groups With *t* and *p*

Your evaluation:

TYPE YOUR ANSWER HERE

# Question 11: Effect Sizes by Group

Your code:

```{r}
# TYPE YOUR CODE HERE
```

Your explanation of the effect sizes:

TYPE YOUR ANSWER HERE

# Question 12: Effect Sizes and the Group-by-Time Interaction

Your answer:

TYPE YOUR ANSWER HERE

# Question 13: Evaluate the *t*-Test Assumptions

AI's code:

```{r}
# PASTE AI'S CODE HERE
```

Your supplement paragraph:

TYPE YOUR ANSWER HERE

# Question 14: Chat Log

`````
PASTE YOUR CHAT LOG HERE
`````
