---
title: "Psych 250a — Week 1 Assignment. Describing Data"
author: "YOUR NAME HERE"
date: "`r format(Sys.Date(), '%B %d, %Y')`"
output:
  pdf_document:
    toc: true
    toc_depth: 3
    latex_engine: xelatex
  html_document:
    toc: true
    toc_float:
      collapsed: false
      smooth_scroll: false
    toc_depth: 3
    theme: cosmo
    highlight: haddock
header-includes:
  - \usepackage{fvextra}
  - \DefineVerbatimEnvironment{Highlighting}{Verbatim}{breaklines,breakanywhere,commandchars=\\\{\}}
  - \fvset{breaklines=true, breakanywhere=true}
  - \RecustomVerbatimEnvironment{verbatim}{Verbatim}{breaklines,breakanywhere}
editor_options:
  chunk_output_type: console
---

```{r include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  message = FALSE,
  warning = FALSE,
  error = TRUE,
  comment = "",
  fig.width = 8,
  fig.height = 5)

options(scipen = 999, width = 80)
```

# Question 1: Import and Summarize the Data

```{r}
# TYPE YOUR CODE HERE
```

# Question 2: Convert ELS and Female to Factors

Your code:

```{r}
# TYPE YOUR CODE HERE
```

# Question 3: Inflammation Sum Score

Your code:

```{r}
# TYPE YOUR CODE HERE
```

# Question 4: Histograms with Density Curves

Your code:

```{r}
# TYPE YOUR CODE HERE
```

# Question 5: TNF Distribution Shape

TYPE YOUR ANSWER HERE

# Question 6: Inflammation Distribution Shape

TYPE YOUR ANSWER HERE

# Question 7: Descriptive Statistics

Your code:

```{r}
# TYPE YOUR CODE HERE
```

Skewness and excess kurtosis for `TNF` and `Inflammation`:

TYPE YOUR ANSWER HERE

# Question 8: TNF Skewness and Kurtosis

TYPE YOUR ANSWER HERE

# Question 9: Inflammation Skewness and Kurtosis

TYPE YOUR ANSWER HERE

# Question 10: AI Prompt for Q–Q Plots

AI's code:

```{r}
# PASTE AI'S CODE HERE
```

# Question 11: Interpret the Q–Q Plot

TYPE YOUR ANSWER HERE

# Question 12: Side-by-Side Histograms by ELS

Your code:

```{r}
# TYPE YOUR CODE HERE
```

# Question 13: AI Suggestions to Improve the Graph

Which suggestion you selected and why it should improve the display:

TYPE YOUR ANSWER HERE

The modified code:

```{r}
# PASTE AI'S CODE HERE
```

# Question 14: Conclusion About ELS and Inflammation

TYPE YOUR ANSWER HERE

# Question 15: Chat Log

`````
PASTE YOUR CHAT LOG HERE
`````
