---
title: "Psych 250a — Week 4 Assignment. Confidence Intervals"
author: "YOUR NAME HERE"
date: "`r format(Sys.Date(), '%B %d, %Y')`"
output:
  pdf_document:
    toc: true
    toc_depth: 3
    latex_engine: xelatex
  html_document:
    toc: true
    toc_float:
      collapsed: false
      smooth_scroll: false
    toc_depth: 3
    theme: cosmo
    highlight: haddock
header-includes:
  - \usepackage{fvextra}
  - \DefineVerbatimEnvironment{Highlighting}{Verbatim}{breaklines,breakanywhere,commandchars=\\\{\}}
  - \fvset{breaklines=true, breakanywhere=true}
  - \RecustomVerbatimEnvironment{verbatim}{Verbatim}{breaklines,breakanywhere}
editor_options:
  chunk_output_type: console
---

```{r include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  message = FALSE,
  warning = FALSE,
  error = TRUE,
  comment = "",
  fig.width = 8,
  fig.height = 5)

options(scipen = 999, width = 80)
```

# Question 1: Import and Summarize the Data

Your code:

```{r}
# TYPE YOUR CODE HERE
```

# Question 2: Convert Female to a Factor

Your code:

```{r}
# TYPE YOUR CODE HERE
```

# Question 3: 95% Confidence Interval for Perceived Discrimination

Your code:

```{r}
# TYPE YOUR CODE HERE
```

# Question 4: Interpret the Confidence Limits

Your interpretation of the lower and upper limits:

TYPE YOUR ANSWER HERE

# Question 5: AI Alternative Explanation of a Confidence Interval

The new idea you selected, in your own words, and how it differs from your Question 4 interpretation:

TYPE YOUR ANSWER HERE

# Question 6: Frequentist Meaning of 95% Confidence

Your evaluation:

TYPE YOUR ANSWER HERE

# Question 7: Frequentist Versus Bayesian Confidence

Your summary of the key difference:

TYPE YOUR ANSWER HERE

# Question 8: Confidence Intervals by Sex

Your code:

```{r}
# TYPE YOUR CODE HERE
```

# Question 9: Compare the Groups

Your answer:

TYPE YOUR ANSWER HERE

# Question 10: Chat Log

`````
PASTE YOUR CHAT LOG HERE
`````
