---
title: "Psych 250a — Week 7 Assignment. Independent-Samples t-Test"
author: "YOUR NAME HERE"
date: "`r format(Sys.Date(), '%B %d, %Y')`"
output:
  pdf_document:
    toc: true
    toc_depth: 3
    latex_engine: xelatex
  html_document:
    toc: true
    toc_float:
      collapsed: false
      smooth_scroll: false
    toc_depth: 3
    theme: cosmo
    highlight: haddock
header-includes:
  - \usepackage{fvextra}
  - \DefineVerbatimEnvironment{Highlighting}{Verbatim}{breaklines,breakanywhere,commandchars=\\\{\}}
  - \fvset{breaklines=true, breakanywhere=true}
  - \RecustomVerbatimEnvironment{verbatim}{Verbatim}{breaklines,breakanywhere}
editor_options:
  chunk_output_type: console
---

```{r include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  message = FALSE,
  warning = FALSE,
  error = TRUE,
  comment = "",
  fig.width = 8,
  fig.height = 5)

options(scipen = 999, width = 80)
```

# Question 1: Import the Data and Convert Factors

Your code:

```{r}
# TYPE YOUR CODE HERE
```

# Question 2: Descriptive Statistics by Condition

Your code:

```{r}
# TYPE YOUR CODE HERE
```

# Question 3: Predict the Baseline Comparison

Your predictions and reasoning:

TYPE YOUR ANSWER HERE

# Question 4: Baseline *t*-Test and Effect Size

Your code:

```{r}
# TYPE YOUR CODE HERE
```

# Question 5: Report the Baseline Comparison

Your passage (no more than two sentences):

TYPE YOUR ANSWER HERE

# Question 6: Week 3 *t*-Test and Effect Size

Your code:

```{r}
# TYPE YOUR CODE HERE
```

# Question 7: AI Prompt for the Bar Graph

AI's code:

```{r}
# PASTE AI'S CODE HERE
```

Your description of each layer (one bullet point per layer):

TYPE YOUR ANSWER HERE

# Question 8: Report the Results in APA Format

Your APA-style passage:

TYPE YOUR ANSWER HERE

# Question 9: AI Prompt on Evaluating Within-Group Normality

No response is needed here; your prompt and AI's response will appear in your chat log in Question 13.

# Question 10: Choose and Implement a Normality Check

Your chosen method and your rationale:

TYPE YOUR ANSWER HERE

AI's code:

```{r}
# PASTE AI'S CODE HERE
```

# Question 11: Assumptions for an Online Supplement

Your supplement paragraph:

TYPE YOUR ANSWER HERE

# Question 12: Interpret the Confidence Interval

Your interpretation of the confidence limits and whether the interval is consistent with the *p*-value:

TYPE YOUR ANSWER HERE

# Question 13: Chat Log

`````
PASTE YOUR CHAT LOG HERE
`````
