---
title: "Psych 250a — Week 2 Assignment. Descriptive Statistics"
author: "YOUR NAME HERE"
date: "`r format(Sys.Date(), '%B %d, %Y')`"
output:
  pdf_document:
    toc: true
    toc_depth: 3
    latex_engine: xelatex
  html_document:
    toc: true
    toc_float:
      collapsed: false
      smooth_scroll: false
    toc_depth: 3
    theme: cosmo
    highlight: haddock
header-includes:
  - \usepackage{fvextra}
  - \DefineVerbatimEnvironment{Highlighting}{Verbatim}{breaklines,breakanywhere,commandchars=\\\{\}}
  - \fvset{breaklines=true, breakanywhere=true}
  - \RecustomVerbatimEnvironment{verbatim}{Verbatim}{breaklines,breakanywhere}
editor_options:
  chunk_output_type: console
---

```{r include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  message = FALSE,
  warning = FALSE,
  error = TRUE,
  comment = "",
  fig.width = 8,
  fig.height = 5)

options(scipen = 999, width = 80)
```

```{r}
library(ggplot2)
library(psych)
library(summarytools)
```

```{r}
# Reads the data from the course repository. Requires an internet connection.
file_url <- "https://raw.githubusercontent.com/craigenders/psych250a/main/data/assignment2.csv"
assign2 <- read.csv(file_url, stringsAsFactors = TRUE)

# To work offline instead, save assignment2.csv to the same folder as this script
# Comment out the lines that read the data from online repository
# Remove the hashtag from the three lines below
# library(rstudioapi)
# setwd(dirname(getActiveDocumentContext()$path))
# assign2 <- read.csv("assignment2.csv", stringsAsFactors = TRUE)
```

# Question 1: Convert ADHD and Male to Factors

Your code:

```{r}
# TYPE YOUR CODE HERE
```

# Question 2: Group Comparison Graphs and Descriptive Statistics

Your code:

```{r}
# TYPE YOUR CODE HERE
```

# Question 3: AlphaEEG Mean Versus Median

TYPE YOUR ANSWER HERE

# Question 4: Attention Group Means and Standard Deviations

TYPE YOUR ANSWER HERE

# Question 5: AI on t-Test Conditions

AI's explanation:

```
PASTE AI'S RESPONSE HERE
```

Your evaluation of which outcome more closely satisfies the conditions, and why:

TYPE YOUR ANSWER HERE

# Question 6: Explain the Standard Deviation

Your original passage:

TYPE YOUR ANSWER HERE

AI's response:

```
PASTE AI'S RESPONSE HERE
```

Whether you accepted or rejected AI's evaluation of each requirement, and why:

TYPE YOUR ANSWER HERE

Your revised passage:

TYPE YOUR ANSWER HERE

# Question 7: z-Scores

Your prompt:

PASTE YOUR PROMPT HERE

AI's explanation:

```
PASTE AI'S RESPONSE HERE
```

Your code:

```{r}
# TYPE YOUR CODE HERE
```

Whether and how your results align with AI's predictions:

TYPE YOUR ANSWER HERE

# Question 8: Comparing Standardized Group Differences

Your code:

```{r}
# TYPE YOUR CODE HERE
```

Your conclusion about which measure shows more pronounced ADHD-related differences:

TYPE YOUR ANSWER HERE
