---
title: "Psych 250a — Week 1 Assignment. Describing Data"
author: "YOUR NAME HERE"
date: "`r format(Sys.Date(), '%B %d, %Y')`"
output:
  pdf_document:
    toc: true
    toc_depth: 3
    latex_engine: xelatex
  html_document:
    toc: true
    toc_float:
      collapsed: false
      smooth_scroll: false
    toc_depth: 3
    theme: cosmo
    highlight: haddock
header-includes:
  - \usepackage{fvextra}
  - \DefineVerbatimEnvironment{Highlighting}{Verbatim}{breaklines,breakanywhere,commandchars=\\\{\}}
  - \fvset{breaklines=true, breakanywhere=true}
  - \RecustomVerbatimEnvironment{verbatim}{Verbatim}{breaklines,breakanywhere}
editor_options:
  chunk_output_type: console
---

```{r include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  message = FALSE,
  warning = FALSE,
  error = TRUE,
  comment = "",
  fig.width = 8,
  fig.height = 5)

options(scipen = 999, width = 80)
```

```{r}
library(ggplot2)
library(psych)
library(summarytools)
```

```{r}
# Reads the data from the course repository. Requires an internet connection.
file_url <- "https://raw.githubusercontent.com/craigenders/psych250a/main/data/assignment1.csv"
assign1 <- read.csv(file_url, stringsAsFactors = TRUE)

# To work offline instead, save assignment1.csv to the same folder as this script
# Comment out the lines that read the data from online repository
# Remove the hashtag from the three lines below
# library(rstudioapi)
# setwd(dirname(getActiveDocumentContext()$path))
# assign1 <- read.csv("assignment1.csv", stringsAsFactors = TRUE)
```

# Question 1: Convert ELS and Female to Factors

Your code:

```{r}
# TYPE YOUR CODE HERE
```

# Question 2: Inflammation Sum Score

Your code:

```{r}
# TYPE YOUR CODE HERE
```

# Question 3: Histograms with Density Curves

Your code:

```{r}
# TYPE YOUR CODE HERE
```

# Question 4: TNF Distribution Shape

TYPE YOUR ANSWER HERE

# Question 5: Inflammation Distribution Shape

TYPE YOUR ANSWER HERE

# Question 6: Descriptive Statistics

Your code:

```{r}
# TYPE YOUR CODE HERE
```

# Question 7: TNF Skewness and Kurtosis

TYPE YOUR ANSWER HERE

# Question 8: Inflammation Skewness and Kurtosis

TYPE YOUR ANSWER HERE

# Question 9: AI Prompt for Q–Q Plots

Your prompt:

PASTE YOUR PROMPT HERE

AI's explanation:

```
PASTE AI'S RESPONSE HERE
```

AI's code:

```{r}
# PASTE AI'S CODE HERE
```

# Question 10: Interpret the Q–Q Plot

TYPE YOUR ANSWER HERE

# Question 11: Side-by-Side Histograms by ELS

Your code:

```{r}
# TYPE YOUR CODE HERE
```

# Question 12: AI Suggestions to Improve the Graph

AI's suggestions:

```
PASTE AI'S RESPONSE HERE
```

Which suggestion you selected and why it should improve the display:

TYPE YOUR ANSWER HERE

The modified code:

```{r}
# PASTE AI'S CODE HERE
```

# Question 13: Conclusion About ELS and Inflammation

TYPE YOUR ANSWER HERE
