---
title: "Psych 250a — Assignment 3: Descriptive Statistics"
author: "YOUR NAME HERE"
date: "`r format(Sys.Date(), '%B %d, %Y')`"
output:
  pdf_document:
    toc: true
    toc_depth: 3
    latex_engine: xelatex
  html_document:
    toc: true
    toc_float:
      collapsed: false
      smooth_scroll: false
    toc_depth: 3
    theme: cosmo
    highlight: haddock
header-includes:
  - \usepackage{fvextra}
  - \DefineVerbatimEnvironment{Highlighting}{Verbatim}{breaklines,breakanywhere,commandchars=\\\{\}}
  - \fvset{breaklines=true, breakanywhere=true}
  - \RecustomVerbatimEnvironment{verbatim}{Verbatim}{breaklines,breakanywhere}
editor_options:
  chunk_output_type: console
---

```{r include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  message = FALSE,
  warning = FALSE,
  error = TRUE,
  comment = "",
  fig.width = 8,
  fig.height = 5)

options(scipen = 999, width = 80)
```

```{r}
library(ggplot2)
library(psych)
library(summarytools)
```

```{r}
# Reads the data from the course repository. Requires an internet connection.
file_url <- "https://raw.githubusercontent.com/craigenders/psych250a/main/data/assignment2.csv"
assign2 <- read.csv(file_url, stringsAsFactors = TRUE)

# To work offline instead, save assignment0.csv to the same folder as this script
# Comment out the lines that read the data from online repository
# Remove the hashtag from the three lines below
# library(rstudioapi)
# setwd(dirname(getActiveDocumentContext()$path))
# assign2 <- read.csv("assignment2.csv", stringsAsFactors = TRUE)
```

# Question 1: Attention sum score

Your code:

```{r}
# TYPE YOUR CODE HERE
```

# Question 2: Factor conversions

Your code:

```{r}
# TYPE YOUR CODE HERE
```

# Question 3: Verification prompt

Your prompt:

PASTE YOUR PROMPT HERE

AI's response:

```
PASTE AI'S RESPONSE HERE
```

AI's code:

```{r}
# PASTE AI'S CODE HERE
```

# Question 4: Group-comparison figures

Your code:

```{r}
# TYPE YOUR CODE HERE
```

# Question 5: Conditions for the independent-samples t-test

AI's response:

```
PASTE AI'S RESPONSE HERE
```

Your code:

```{r}
# TYPE YOUR CODE HERE
```

Your explanation:

TYPE YOUR ANSWER HERE

# Question 6: Standard deviation passage and AI critique

Your original passage:

TYPE YOUR ANSWER HERE

AI's response:

```
PASTE AI'S RESPONSE HERE
```

Whether you accepted or rejected AI's evaluation of each requirement, and why:

TYPE YOUR ANSWER HERE

Your revised passage:

TYPE YOUR ANSWER HERE

# Question 7: Standardized scores

Your prompt:

PASTE YOUR PROMPT HERE

AI's response:

```
PASTE AI'S RESPONSE HERE
```

Your code:

```{r}
# TYPE YOUR CODE HERE
```

Whether and how your results align with AI's predictions:

TYPE YOUR ANSWER HERE

# Question 8: Conclusion

TYPE YOUR ANSWER HERE
