---
title: "Week 0 Example: Cancer Data"
author: "YOUR NAME"
date: "`r format(Sys.Date(), '%B %d, %Y')`"
output:
  html_document:
    toc: true
    toc_float:
      collapsed: false
      smooth_scroll: false
    toc_depth: 2
    theme: cosmo
    highlight: haddock
  pdf_document:
    toc: true
    toc_depth: 2
    latex_engine: xelatex
header-includes:
  - \usepackage{fvextra}
  - \DefineVerbatimEnvironment{Highlighting}{Verbatim}{breaklines,breakanywhere,commandchars=\\\{\}}
  - \fvset{breaklines=true, breakanywhere=true}
  - \RecustomVerbatimEnvironment{verbatim}{Verbatim}{breaklines,breakanywhere}
editor_options:
  chunk_output_type: console
---

```{r include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  message = FALSE,
  warning = FALSE,
  error = TRUE,
  comment = "",
  fig.width = 8,
  fig.height = 5)

options(scipen = 999, width = 80)
```

# Loading Packages

The summarytools package provides dfSummary() for data summaries.

```{r}
# summarytools provides dfSummary() for data summaries
library(summarytools)
```

# Importing Data

The data file lives on the course GitHub site. Store the web address in an
object, then hand that address to read.csv().

```{r}
# store the web address of the raw data file
filepath <- "https://raw.githubusercontent.com/craigenders/psych250a/main/data/Cancer.csv"

# read the file at that address into a data frame named Cancer
Cancer <- read.csv(filepath, stringsAsFactors = TRUE)
```

# Converting Categorical Variables to Factors

Diagnosis and Male are stored as 0/1 codes. factor() converts each one
to a categorical variable with descriptive labels.

```{r}
# convert Diagnosis from 0/1 codes to a factor with descriptive labels
Cancer$Diagnosis <- factor(Cancer$Diagnosis,
                           levels = c(0, 1),
                           labels = c("Non-malignant", "Malignant"))

# convert Male from 0/1 codes to a factor with descriptive labels
Cancer$Male <- factor(Cancer$Male,
                      levels = c(0, 1),
                      labels = c("Female", "Male"))

# print the first few rows to confirm the labels replaced the codes
head(Cancer)
```

# Summarizing Data

dfSummary() gives an overview of every variable in the data frame.

```{r}
# overview of every variable in the data frame
dfSummary(Cancer)
```
