---
title: "Week 2 Data Blitz: Comparing Groups"
author: "GROUP MEMBER NAMES"
date: "`r format(Sys.Date(), '%B %d, %Y')`"
output:
  html_document:
    toc: true
    toc_float:
      collapsed: false
      smooth_scroll: false
    toc_depth: 2
    theme: cosmo
    highlight: haddock
editor_options:
  chunk_output_type: console
knit: (function(input, ...) rmarkdown::render(input, output_file = xfun::with_ext(basename(input), "html"), output_dir = dirname(input)))
---

```{r include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  message = FALSE,
  warning = FALSE,
  error = TRUE,
  comment = "",
  fig.width = 8,
  fig.height = 5)

options(scipen = 999, width = 80)
```

# Loading Packages

```{r}
library(ggplot2)
library(psych)
library(summarytools)
```

# Reading the Data

```{r}
filepath <- "https://raw.githubusercontent.com/craigenders/psych250a/main/data/FILENAME.csv"
blitz <- read.csv(filepath, stringsAsFactors = TRUE)
```

# 1. Research Question

TYPE YOUR ANSWER HERE

# 2. Factor Conversion and Frequency Distribution

Your code:

```{r}
# TYPE YOUR CODE HERE
```

# 3. Group-Comparison Histograms

Your code:

```{r}
# TYPE YOUR CODE HERE
```

# 4. AI Graph Recommendations

Your prompt and AI's response:

```
PASTE YOUR PROMPT AND AI'S RESPONSE HERE
```

# 5. Alternative Graph

Which recommendation you selected and why:

TYPE YOUR ANSWER HERE

Your prompt and AI's response:

```
PASTE YOUR PROMPT AND AI'S RESPONSE HERE
```

AI's code:

```{r}
# PASTE AI'S CODE HERE
```

What this display reveals that was difficult to see in the histograms:

TYPE YOUR ANSWER HERE

# 6. Presentation-Ready Graph

Your prompt and AI's response:

```
PASTE YOUR PROMPT AND AI'S RESPONSE HERE
```

AI's code:

```{r}
# PASTE AI'S CODE HERE
```

# 7. Descriptive Statistics by Group

Your code:

```{r}
# TYPE YOUR CODE HERE
```

How the means and standard deviations show up in the graphs:

TYPE YOUR ANSWER HERE

# 8. Distributional Conditions for ANOVA

Your prompt and AI's response:

```
PASTE YOUR PROMPT AND AI'S RESPONSE HERE
```

Your evaluation of the conditions:

TYPE YOUR ANSWER HERE

# 9. Conclusion

TYPE YOUR ANSWER HERE
